---
author: Wesley & Ritika
title: Users with High Score
---

```{r init ,echo=FALSE}
#load("../data/data.Rdata")
library(magrittr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(recommendR)
```

# Exploratory Analysis

There were a total of `r nrow(behave)` user behaviour records with `r length(unique(behave$user_id))` users coming from 
`r length(unique(users$countries))`.

```{r Big-table, cache=TRUE}
userdetails_all     <- merge(behave, users, by="user_id", all.x=TRUE)
user_video_nocast   <- merge(userdetails_all, videos_attributes, by="video_id", all.x=TRUE)
```

We found the total score for each user and named it `totalScore`.

```{r grouping, cache=TRUE}
#group the users by Score country and gender
uu2 <- user_video_nocast               %>%
        group_by(user_id)              %>%
        summarise(
            totalScore = sum(score),
            freq = n(),
            country = unique(country),
            gender = unique(gender))   %>%
        arrange(desc(totalScore))
```

Next we looked at the various quantiles for `totalScore` and found that categorised users into two categories

```{r}
quantile(uu2$totalScore, c(0,0.25,0.5,0.75,1))
```

| Category | Description                                                                                  |
| ---      | ---                                                                                          |
| HiScore  | Users >= 80 percentile (based on score). They have 60% of total views (need so suptantiate)  |
| LowScore | Users < 80 percentile (based on score)                                                       |

## High Score Users

```{r}
hiScore      <- subset(uu2, totalScore >= 20)
hiScoreVideo <- subset(user_video_nocast, user_id %in% unique(hiScore$user_id))
```

We decided to further segment the scores into 4 categories

| newScore | range               |
| ---      | ---                 |
| 1        | mv_ratio < 20       |
| 2        | 20 <= mv_ratio < 50 |
| 3        | 50 <= mv_ratio < 80 |
| 4        | mv_ratio >= 80 |

```{r echo=FALSE}
dff <-  hiScoreVideo %>%
        transmute(
            mv_ratio = mv_ratio,
            video_id = video_id,
            user_id = user_id,
            Score1 = (mv_ratio < 20 )*1,
            Score2 = (mv_ratio >= 20 & mv_ratio <50)*1,
            Score3 = (mv_ratio >= 50 & mv_ratio < 80)*1,
            Score4 = (mv_ratio >= 80)*1) %>% 
        gather(scoreType, value, -video_id, -user_id, -mv_ratio) %>% 
        filter(value > 0 ) %>% select(-value)
#Change scoreType to integers

        dff$scoreType %<>% factor(labels=c("1", "2", "3", "4"))
        dff$scoreType %<>% as.character %>% as.integer
        colnames(dff)[4] = "scoreNew" #rename a col
#merging with dff to get new score variables
hiScoreVideo_new <- merge(hiScoreVideo, dff, by = c("user_id","video_id", "mv_ratio"),all=TRUE)
```

## Segmenting by Frequency

```{r}
##Segmenting High Score Users by Frequency
hiScoreByFreq <-    hiScoreVideo_new %>%
    group_by(user_id)                %>%
    summarise(freq          = n(),
              totalScore    = sum(score),
              totalScoreNew = sum(scoreNew),
              country       = unique(country),
              gender        = unique(gender)
              )
quantile(hiScoreByFreq$freq, seq(0,1,0.05)) 
```

We segment the users into the 95, 65-95, < 65 percentiles.

```{r}
#making different df by Freq (95%ile & above; 65-95 %ile; < 65%ile)
hiScoreHiFreq  <- subset(hiScoreByFreq, freq >= 40)
hiScoreMoFreq  <- subset(hiScoreByFreq, freq >= 20 & freq <40)
hiScoreLowFreq <- subset(hiScoreByFreq, freq < 20)
# with video details
hiScHiFreqVideo  <- subset(hiScoreVideo_new, hiScoreVideo$user_id %in% hiScoreHiFreq$user_id)
hiScMoFreqVideo  <- subset(hiScoreVideo_new, hiScoreVideo$user_id %in% hiScoreMoFreq$user_id)
hiScLowFreqVideo <- subset(hiScoreVideo_new, hiScoreVideo$user_id %in% hiScoreLowFreq$user_id)
```

## Ranking the users

```{r}
#*** RANKING CODE (based on the new scoring scheme - scoreNew)

hiScHiFreqRankNew <- hiScHiFreqVideo %>% group_by(video_id) %>% 
summarise(
  totalviews     = n(), 
  scoreNew1views = sum(scoreNew == "1")/n(), 
  scoreNew2views = sum(scoreNew=="2")/n(), 
  scoreNew3views = sum(scoreNew=="3")/n(), 
  scoreNew4views = sum(scoreNew=="4")/n(), 
  RankingNew     = ((scoreNew1views*1+scoreNew2views*2+scoreNew3views*3+ scoreNew4views*4)* (scoreNew3views+scoreNew4views)*totalviews)
  ) %>%
arrange(desc(RankingNew))
```

We check to see if the new ranking system has an effect

```{r compareRanking}
##Plot both old and new rankings and score views
hiScHiFreqRankNew <- merge(hiScHiFreqRankNew, hiScHiFreqRankOld %>% select(video_id, RankingOld) , by = "video_id", all.x = TRUE)

## Plot for New Ranking (with a line for Old Ranking as well)

#Set Factor levels
hiScHiFreqRankNew %<>% arrange(desc(RankingNew))
hiScHiFreqRankNew$video_id %<>% factor(levels = as.character(hiScHiFreqRankNew$video_id))

hiScHiFreqRankNew_long <- hiScHiFreqRankNew %>%
    gather(scoreType, value, -video_id, -totalviews, -RankingNew, -RankingOld)

rankDFNew <- hiScHiFreqRankNew_long %>% select(video_id, RankingNew, RankingOld) %>% unique
rankDFNew %<>% gather(rankType, value, -video_id)
```

```{r scoreTypeRankingNEW2}
#  pdf("../out/.pdf", w=20)
hiScHiFreqRankNew_long %>% 
    mutate(newValue = value * totalviews) %>% 
    ggplot(aes(x=video_id, y=newValue))                                                                                                 +
        geom_line(aes(group=scoreType, color=scoreType))                                                                                +
        geom_line(data=rankDFNew, inherit.aes=FALSE, aes(video_id, value/2, group=rankType, linetype=rankType), color="black",size=0.5) +
        ylab("Totalviews")                                                                                                              +
        ggtitle("New ranking")
#  dev.off() 
```

```{r}
## Plot for Old Ranking** No Need to run til you want to look at the details
  
hiScHiFreqRankOld <- hiScHiFreqVideo %>%
group_by(video_id) %>%
    summarise(
      totalviews   =  n(),
      score1views  =  sum(score == "1")/n(),
      score2views  =  sum(score=="2")/n(),
      score3views  =  sum(score=="3")/n(),
      RankingOld   =  ((score1views*1+score2views*2+score3views*3)*(score2views+score3views)*totalviews)
)%>% 
arrange(desc(RankingOld))
  
hiScHiFreqRankOld %<>% arrange(desc(RankingOld))
hiScHiFreqRankOld$video_id = factor(hiScHiFreqRankOld$video_id, levels = as.character(hiScHiFreqRankOld$video_id))
  
hiScHiFreqRankOld_long = hiScHiFreqRankOld %>%
gather(scoreType, value, -video_id, -totalviews, -RankingOld)
  
rankDFOld = hiScHiFreqRankOld_long %>% select(video_id, RankingOld) %>% unique
```

```{r scoreTypeRankingOLD}
#  pdf("../out/.pdf", w=20) 
hiScHiFreqRankOld_long                %>%
mutate(newValue = value * totalviews) %>%
ggplot(aes(x=video_id, y=newValue))                                 +
    geom_line(aes(group=scoreType, color=scoreType))                +
    geom_line(data=rankDFOld,
        aes(video_id, RankingOld/2, group=1),
        inherit.aes=FALSE, color="black", size=1.5)                 +
    ylab("Totalviews")                                              +
    ggtitle("Old ranking")
#  dev.off()
```

```{r noNeed, eval=FALSE, echo=FALSE}
##seeing country wise behaviour for the top countries
  
## pattern by Country of User
hiScoreHiFreq %>% group_by(country) %>% 
    summarise(CountryFreq = sum(freq), CountryScore = sum(totalScore), 
              f=sum(gender=="f"),m=sum(gender=="m"), o=sum(gender=="o"), N=sum(gender=="None"),
              total = n())%>% arrange(desc(CountryFreq)) %>% head(n=1)

subset(hiScHiFreqVideo, country == "Country001") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender)
```

## High-Score High-Freq 

Segmented by gender, score, Frequency

```{r eval=FALSE, echo=FALSE}
group_by(country)                   %>%
summarise(
    CountryFreq = sum(freq),
    CountryScore = sum(totalScore),
    f=sum(gender=="f"),
    m=sum(gender=="m"),
    o=sum(gender=="o"),
    N=sum(gender=="None"),
    total = n()
    )                               %>%
arrange(desc(CountryFreq))          %>%
head(n=15)

#**********************************************************************
#freq Score and User Profiles by Country ***** Results

country CountryFreq CountryScore    f   m  o    N total
1  Country001      184456       353014 1777 335 10 1582  3704
2  Country010       31012        57972  435  42  0  139   616
3  Country002       23698        45259  295  33  2  148   478
4  Country003       18618        34603  195  20  0  151   366
5  Country007       17070        32601  252  24  0   59   335
6  Country014       12975        24884  145  19  0  101   265
7  Country009        9546        17655  150   9  0   38   197
8  Country045        8300        16137  121  13  0   33   167
9  Country018        8046        14675  109   7  0   42   158
10 Country004        7996        14851   94  10  1   51   156
11 Country015        7287        13997  106   3  0   38   147
12 Country011        6866        12911  111   6  0   21   138
13 Country021        6437        11970   80   6  0   42   128
14 Country035        4157         7834   66   6  1   14    87
15 Country022        3578         6418   43   2  1   26    72


##PDF of the graphs (originCountry_Score_by Gender)
pdf("~/Desktop/VideoByCountry.pdf")
subset(hiScHiFreqVideo, country == "Country001") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country001")

> subset(hiScHiFreqVideo, country == "Country010") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country010")

> subset(hiScHiFreqVideo, country == "Country002") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country002")

> subset(hiScHiFreqVideo, country == "Country003") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country003")

> subset(hiScHiFreqVideo, country == "Country007") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country007")

> subset(hiScHiFreqVideo, country == "Country014") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country014")
> subset(hiScHiFreqVideo, country == "Country009") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country009")
> subset(hiScHiFreqVideo, country == "Country045") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country045")
> subset(hiScHiFreqVideo, country == "Country018") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country018")
> subset(hiScHiFreqVideo, country == "Country004") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country004")
> subset(hiScHiFreqVideo, country == "Country015") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country015")
> subset(hiScHiFreqVideo, country == "Country011") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country011")
> subset(hiScHiFreqVideo, country == "Country021") %>% group_by(origin_country, gender) %>% summarise(totalScore = sum(score)) %>% ggplot(aes(reorder(origin_country, totalScore), totalScore))+geom_boxplot()+ aes(color = gender) +ggtitle("Country021")
> dev.off()
```

## Session Infomation

```{r echo=FALSE}
sessionInfo()
```
