```{r libraries, echo=FALSE}
suppressMessages(library(magrittr))
suppressMessages(library(stringr))
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
theme_set(theme_bw())
```

## Disclaimer: 
Records only includes cases where User began watching from Episode1

- Even if user watched the video many times, only one record is there but total watched time increases
- Includes only registered user
- Watching time of a particular video is an aggregate of the time (Oct to Jan)
- mv_ratio = watched time * 100/total duration
- score = mv_ratio<20; 20<..<80; >80 (equivalent scores - 1,2,3)
- each container is a video series
- each video is not available in al the countries
- total 632 videos

## Summary

* mv_ratio 
* score 

>NOTE:: Country is masked

geoblock (only some of the countries are available)
TV series are also availble in limited countries

```{r behavior, eval=FALSE}
behave      = data.table::fread("../data/Behavior_training.csv")
dateTime    = behave$date_hour %>% 
                str_split(pattern="T") %>% 
                do.call(rbind,.) %>% 
                as.data.frame %>% setNames(c("date", "time"))

dateTime    %<>% mutate(date = lubridate::ymd(date))
behave      %<>% cbind(dateTime)
str(behave)
```

* recommendation will only make sense for people who only watched one episode
* 



```{r users, eval=FALSE}
users  = read.csv("../data/User_attributes.csv")
str(users)
```

```{r videos, eval=FALSE}
videos_attributes = read.csv("../data/Video_attributes.csv", h = T)
str(videos_attributes)

videos_casts      = read.csv("../data/Video_casts.csv", h = T)
videos_casts %<>% setNames(c("contained_id", "cast_person_id","country", "casts_gender"))
str(videos_casts)
```

```{r save, eval=FALSE}
save(behave, users, videos_attributes, videos_casts, file="../data/data.Rdata")
```

```{r}
load(file="../data/data.Rdata")
```

## Checking

```{r season}
videos_attributes %>% ggplot(aes(season_number)) + 
  geom_bar()
```

```{r country}
countryTable = users$country %>% 
table %>% 
as.data.frame %>% 
setNames(c("country", "freq")) %>% 
arrange(desc(freq))

i=0
a=0
sapply(countryTable$freq, function(freq){

       
       if(i < sum(countryTable$freq) * 0.95){
       i <<- i + freq
       a <<- a+ 1
       }
})

#quantile(countryTable$freq, c(seq(0.05, 0.95, by=0.05)))


users %>% ggplot(aes(country)) + geom_bar()

countryFreq = users$country %>% table %>% as.data.frame %>% setNames(c("country", "freq"))
ggplot(countryFreq, aes(reorder(country, freq), freq)) + geom_bar(stat="identity") + scale_y_log10()



filter(countryFreq, freq > 1) %>% nrow
```

* find countries with 95% for counts or time 
* he likes viki (Num of videos he watchs), but if the time is short the videos arent matchin his expectation. 
